---
title: ""
author: "Claudia Solis-Roman"
date: "March 8, 2020"
output: html_document
---

#Ravi clas proj - Texas stops & race classification 
tx1  
csr315@nyu.edu  mvb
DUE: MONDAY MAY 11

 dta: https://openpolicing.stanford.edu/data/  
 doc: https://github.com/stanford-policylab/opp/blob/master/data_readme.md
 code: https://github.com/stanford-policylab/opp/tree/master/lib

 progs: 
   1 Looking at Texas state data.R
   2 Downloading census data.R
   3 Merging census data with Texas data
   4 Clean Texas state data
   5 Create descriptive tables
   6 Run regressions

#outline of report
clearly state and motivate your project/research question/policy evaluation idea, 
summarize related academic literature, 
describe your methods, 
detail your results (with the appropriate plots), and 
discuss the implications of your findings. 
Unless you receive permission for an exception from the instructor, you must also include a section discussing potential ethical implications or concerns related to the project .

#outline of models to use

Models
Predict misclassification:
Outcomes
  Misclassification type H-W -- white/other
  No Misclassification (H-H)

Covariates
  Year
  County
  Sex of subject
  Officer is hispanic
  Violation recode into categories (e.g. speeding)
  Speeding
  Stop sign
  Red light
  DUI
  Tail light or head lamp
  Med income age in geog level
  Med age in geog level
  %hisp in geog level ***
  %white in geog level
  %black in geog level
  Dummy majority nonwhite in geog level
  Dummy urban/nonwhite in geog level
  Maybe crime 
  RS: maybe characteristics of stop - ..time of day / 

Predict Hit rate:
Outcomes
  Found contraband weapon/searches
  Found contraband drugs/searches
  Found contraband any/searches
Covariates
  Same as above


Other ideas
Veil of darkness
RS: contraband found hit rates - does this vary by misc cat
Demographics of person stopped varies by if state patrol data (city omre likely to be close to home)
Discrepancies of hit rates - view all at once - see plots used in paper
Points along 45 deg line along location. Sized by 
Frisky - plot 3A and plot B precinct or prejudice. X axis: proportion of residents that are hispanic. Y axis: misclassification rates. Prop classified as white. H: more hispanics, more misclassification rate


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#no code shown or run
```

```{r}

```

## Including Plots

```{r pressure, echo=FALSE}
#plots but no code
plot(pressure)
```

