---
title: ""
author: "Claudia Solis-Roman"
date: "March 8, 2020"
output: html_document
---

#Ravi clas proj - Texas stops & race classification 
tx1  
csr315@nyu.edu  mvb
DUE: MONDAY MAY 11

 dta: https://openpolicing.stanford.edu/data/  
 doc: https://github.com/stanford-policylab/opp/blob/master/data_readme.md
 code: https://github.com/stanford-policylab/opp/tree/master/lib

 progs: 
   1 Looking at Texas state data.R
   2 Downloading census data.R

#outline of report
clearly state and motivate your project/research question/policy evaluation idea, 
summarize related academic literature, 
describe your methods, 
detail your results (with the appropriate plots), and 
discuss the implications of your findings. 
Unless you receive permission for an exception from the instructor, you must also include a section discussing potential ethical implications or concerns related to the project .



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#no code shown or run
```

```{r}

```

## Including Plots

```{r pressure, echo=FALSE}
#plots but no code
plot(pressure)
```

